Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-06-25 paper.tex
Add Matt's grant number

\subsubsection*{Acknowledgements}
This work was supported in part by the National Science Foundation under Grant
No.\ \lstinline{PHY-1430152} (JINA Center for the Evolution of the Elements)
[MBD, YLZ, GCM];
by NASA through the Hubble Fellowship under grant \lstinline{51344.001-A},
awarded by the Space Telescope Science Institute,
which is operated  by the Association of Universities for Research in Astronomy Inc.\
for NASA under contract \lstinline{NAS 5-26555} [EO];
by NASA through the Einstein Postdoctoral Fellowship grant \lstinline{PF4-150122}
awarded by the Chandra X-ray Center,
which is operated by the Smithsonian Astrophysical Observatory for NASA
under contract \lstinline{NAS8-03060},
and through grant \lstinline{80NSSC18K0565} [FF];
and through the U.S.\ Department of Energy, Office of Science,
Office of Nuclear Physics,
under award number \lstinline{DE-FG02-02ER41216} [GCM].
We thank James P.\ Kneller his original flavor evolution code base.
We thank the Spectral Einstein Code collaboration
\footnote{\url{https://www.black-holes.org/code/SpEC.html}} for a powerful and
robust numerical relativity code base, and in particular
Lawrence E.\ Kidder, Daniel A.\ Hemberger, Fran\c{c}ois H\'{e}bert,
and Fatemeh Hossein Nouri for comments and help throughout.
We also thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
and Luke Roberts for helpful discussions at the JINA-CEE Frontiers meeting 2017.

>>>>

\subsubsection*{Acknowledgements}
This work was supported in part by the National Science Foundation under Grant
No.\ \lstinline{PHY-1430152} (JINA Center for the Evolution of the Elements)
[MBD, YLZ, GCM];
by NASA through the Hubble Fellowship under grant \lstinline{51344.001-A},
awarded by the Space Telescope Science Institute,
which is operated  by the Association of Universities for Research in Astronomy Inc.\
for NASA under contract \lstinline{NAS 5-26555} [EO];
by NASA through the Einstein Postdoctoral Fellowship grant \lstinline{PF4-150122}
awarded by the Chandra X-ray Center,
which is operated by the Smithsonian Astrophysical Observatory for NASA
under contract \lstinline{NAS8-03060},
and through grant \lstinline{80NSSC18K0565} [FF];
through National Science Foundation Grant \lstinline{PHY-1402916} [MDD];
and through the U.S.\ Department of Energy, Office of Science,
Office of Nuclear Physics,
under award number \lstinline{DE-FG02-02ER41216} [GCM].
We thank James P.\ Kneller his original flavor evolution code base.
We thank the Spectral Einstein Code collaboration
\footnote{\url{https://www.black-holes.org/code/SpEC.html}} for a powerful and
robust numerical relativity code base, and in particular
Lawrence E.\ Kidder, Daniel A.\ Hemberger, Fran\c{c}ois H\'{e}bert,
and Fatemeh Hossein Nouri for comments and help throughout.
We also thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
and Luke Roberts for helpful discussions at the JINA-CEE Frontiers meeting 2017.
